Gravitational wave sensitivity curves

### 2014-07-29 Sources.tex
first para of sec 5, rewritten to be clearer about exactly how the source boxes should be interpretted

All the sources described here are represented by shaded boxes in \ref{app:a}. The boxes are drawn in such a way that there is a reasonable event rate for sources at a detectable SNR. Descriptions of each source are given in the following sections. Sources with short durations (i.e., burst sources) and sources that evolve in time over much longer timescales than our observations are drawn with flat-topped boxes for $h_\mathrm{c}(f)$. Inspiralling binaries, or stochastic backgrounds of binaries, are drawn with a sloping top proportional to $f^{-2/3}$ for $h_\mathrm{c}(f)$, which is result derived in section \ref{sec:stoch}. The width of the box gives the range of frequencies sources of a given type can have while remaining at a detectable amplitude.

>>>>

%All the sources described here are represented by shaded boxes in \ref{app:a}. The boxes are drawn in such a way that there is a reasonable event rate for sources at a detectable SNR. Descriptions of each source are given in the following sections. Sources with short durations (i.e., burst sources) and sources that evolve in time over much longer timescales than our observations are drawn with flat-topped boxes for $h_\mathrm{c}(f)$. Inspiralling binaries, or stochastic backgrounds of binaries, are drawn with a sloping top proportional to $f^{-2/3}$ for $h_\mathrm{c}(f)$, which is result derived in section \ref{sec:stoch}. The width of the box gives the range of frequencies sources of a given type can have while remaining at a detectable amplitude.

All the sources described here are represented by shaded boxes in \ref{app:a}. Sources with short durations (i.e., burst sources) and sources that evolve in time over much longer timescales than our observations are drawn with flat-topped boxes for $h_\mathrm{c}(f)$. Inspiraling binaries, or stochastic backgrounds of binaries, are drawn with a sloping top proportional to $f^{-2/3}$ for $h_\mathrm{c}(f)$, which is result derived in section \ref{sec:stoch}. The width of the box gives the range of frequencies sources of a given type can have while remaining at a detectable amplitude. The question of the height of the box is more problematic; it would be desirable to normalise each box so that there was a fixed event rate, say one event per year with an amplitude lying within the box. However for many of the sources considered the event rate is subject to a large degree of uncertainty (and estimates change rapidly as our understanding of the astrophysics improves). So instead we take the more definite, but somewhat arbitrary, approach that for each type of source a fiducial event is nominated (with parameters or amplitude detailed in the relevant section below) and the amplitude of this event is used to position the top of the box. The parameters for each fiducial event are chosen such that the resulting amplitude is roughly consistent with the maximum end of current predictions. I.e. the boxes indicate where we \emph{could} find GW sources; the actual event rates could turn out to be substantially lower than this upper bound.
